Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-04-29 overleaf/compiler.tex
Minor edits in Intro and Front End

\section{\bf Compiler Framework}
\label{sec:compiler}

@@

\figref{fig:compiler_framework} presents an overview of our compiler.
We start the section with a brief description of the top-level syntax and semantic restrictions.
We proceed to describe several phases of the compiler:~\secref{sec:imp_to_ssa}
describes translation from IMP Source to SSA, and~\secref{sec:ssa_to_MPC_Source}
describes translation form SSA into MPC Source, i.e., the front-end of our compiler.
Finally,~\secref{sec:MOTION} describes translation of MPC Source, un-optimized and
optimized into MOTION, i.e., this is the back-end of our compiler.

Analysis on MPC Source and vectorization comes in a separate section, Section~\secref{sec:vectorization}.
%\ana{Need to state this more precisely.}

@@

\subsection{From (Optimized) MPC Source to MOTION}
\label{sec:MOTION}

@@

% Tons of copies != runtime costs
Due to the SSA translation phase as well as the conversions to and from SIMD values which our utility functions perform, our generated vectorized MOTION code often includes multiple copies of arrays and scalar values.  These copies do not incur a runtime cost as the arrays simply hold \emph{pointers} to the underlying shares, so no new shares or gates are created as a result of this copying. Cost in MPC programs is dominated by shares and computation on shares. %\ben{Is there anything else to say here?  Should this be placed somewhere else?} \ana{It is clear to me! Will stay in the TR but likely will be cut from the paper.}

>>>>

\section{\bf Compiler Front End}
\label{sec:compiler}

@@

\figref{fig:compiler_framework} presents an overview of our compiler.
We start the section with a brief description of the top-level syntax and semantic restrictions in~\secref{sec:syntax}.
We proceed to describe the front end of the compiler:~\secref{sec:imp_to_ssa}
describes translation from IMP Source to SSA, and~\secref{sec:ssa_to_MPC_Source}
describes translation form SSA into MPC Source.

We describe analysis on MPC Source and backend-independent vectorization in~\secref{sec:vectorization}
and translation into MOTION code in~\secref{sec:backend}.
%\ana{Need to state this more precisely.}

@@

\begin{comment}
\subsection{From (Optimized) MPC Source to MOTION}
\label{sec:MOTION}

@@

% Tons of copies != runtime costs
Due to the SSA translation phase as well as the conversions to and from SIMD values which our utility functions perform, our generated vectorized MOTION code often includes multiple copies of arrays and scalar values.  These copies do not incur a runtime cost as the arrays simply hold \emph{pointers} to the underlying shares, so no new shares or gates are created as a result of this copying. Cost in MPC programs is dominated by shares and computation on shares. %\ben{Is there anything else to say here?  Should this be placed somewhere else?} \ana{It is clear to me! Will stay in the TR but likely will be cut from the paper.}
\end{comment}

### 2022-04-29 overleaf/introduction.tex
Minor edits in Intro and Front End

The rest of the paper is organized as follows. \secref{sec:overview} presents an overview of the compiler. \secref{sec:model} describes our model for cost estimation and argues NP-hardness of optimal scheduling. \secref{sec:compiler} details the phases of the compiler and \secref{sec:vectorization} focuses in on vectorization. \secref{sec:results} presents the experimental evaluation.\secref{sec:related} discusses related work and \secref{sec:conclusion} concludes.

>>>>

The rest of the paper is organized as follows. \secref{sec:overview} presents an overview of the compiler. \secref{sec:model} describes our model for cost estimation and argues NP-hardness of optimal scheduling. \secref{sec:compiler} details the front-end phases of the compiler, \secref{sec:vectorization} focuses in on backend-independent vectorization, and \secref{sec:backend} describes translation into MOTION. \secref{sec:results} presents the experimental evaluation.\secref{sec:related} discusses related work and \secref{sec:conclusion} concludes.
